\section{Introcution} \label{sec::introduction}

%\Marjan{Add your comments in others' sections in color}\Ehsan{blue}\Fatem{green}

%Message of the paper: The actor-based language, Rebeca, provides a usable and analyzable model for distributed, concurrent, event-based asynchronous systems (Cyber-Physical systems).

%Distributed systems  are defined like this
%IBM: A distributed computer system consists of multiple software components that are on multiple computers, but run as a single system. The computers that are in a distributed system can be physically close together and connected by a local network, or they can be geographically distant and connected by a wide area network. ...distributed system contains multiple nodes that are physically separate but linked together using the network. All the nodes in this system communicate with each other and handle processes in tandem. Each of these nodes contains a small part of the distributed operating system software.

Distributed systems consist of software components executed on different computers that are linked together by a network. The software components communicate with each other in order to achieve the goal of the distributed system.
Nowadays distributed systems are everywhere providing scalability and redundancy.  Design and analysis of such systems is overly challenging.

%Reactive systems are defined like this
%Actor-based languages and distributed systems
Actor model is a model of concurrent computation for developing parallel, distributed and mobile systems \cite{Hewitt:77:Actors,Agha:97:ActorComputation}. Each actor is an autonomous object that operates concurrently, and  send and receive messages asynchronously.
%
Rebeca \cite{DBLP:journals/fuin/SirjaniMSB04,DBLP:conf/fmco/Sirjani06} is an actor-based language proposed to bridge the gap between software engineers and formal methods community.
Rebeca comes with a formal semantics and is the first actor-based language with model checking support \cite{DBLP:journals/csur/BoerSHHRDJSKFY17}.


Models can be used for both synthesis and analysis \cite{DBLP:conf/facs2/LeeS18}. We build abstract models that serve as a specification of a system to be built, and then we refine the models, adding
details until we build the system itself. The process is usually iterative, with
the specifications evolving along with their refinements. We may have different analysis purposes like verification, validation, and performance evaluation. 
Model checking, simulation, and building physical prototypes can all be used as methods for analysis. Simulation, which is the execution of an executable
model, reveals one possible behavior of a model with one set of inputs. Model
checking reveals all possible behaviors of a model over a family of inputs \cite{DBLP:conf/facs2/LeeS18}.
%If we have formal and automatic refinement techniques, we may be able to avoid introducing errors in the refined models while details are added. In this case, synthesis is said to be “correct by construction.”


%Why actors are good models for distributed systems?
%\noindent\textbf{Faithful models for distributed reactive systems} %\label{sec::Faithfulness}
%How models shape the thought and ease the analysis

%From Rocco paper: 
According to De Nicola et.al. in \cite{DBLP:conf/coordination/NicolaFPT18} a major challenge in designing languages is to devise appropriate abstractions and linguistic primitives to deal with the specificities of the domain under investigation.
%
%From Gul and Rajesh: 
%http://web.cs.ucla.edu/~palsberg/course/cs239/papers/karmani-agha.pdfA 
Karmani and Agha believe that a programming language should facilitate the process of writing programs by being close to the conceptual level at which a programmer thinks about a problem, rather than at the level at which it may be implemented \cite{DBLP:reference/parallel/KarmaniA11}.
%
In \cite{DBLP:conf/birthday/FriendlinessSirjani18}, Sirjani defines faithfulness as the similarity of the
model and the system; and it is argued that faithfulness can bring in analizability and tracability. 
According to \cite{DBLP:conf/birthday/FriendlinessSirjani18}, a modeling
language is faithful to a system if the model of computation supported by the
language matches the model of computation of [the features of interest of] the
system. 
In \cite{Ptolemy:14:Book} a model of computation (MoC) is defined as a collection of rules that govern
the execution of the [concurrent] components and the communication between
components.
Faithfulness can be seen as the key motivation behind domain-specific
languages.

%\Marjan{Here I should add: Rebeca is designed to be faithful to ... At the same time we considered analyzability and so keeping things as simple as possible.Theories and tools are developed (cite papers). Rebeca is used in different applications (cite papers), and each application we devised new techniques mostly using the adavntage of isolation.}

Rebeca stands for \textit{Reactive Objects Language}, and is designed as a \textit{faithful} language for  distributed reactive software systems.
It is an imperative actor-based language while original actor languages are mainly functional languages. It is an event-driven and asynchronous language, with implicit receive and non-blocking send statement. There is no shared variables, and methods are atomic and run to completion.
A  tool suite for model checking is available at \cite{RebecaSite}. Theories, techniques and tools for compositional verification \cite{DBLP:journals/jucs/SirjaniMSB05}, symmetry and partial order reduction \cite{DBLP:journals/acta/JaghooriSMKM10}, and slicing \cite{DBLP:journals/scp/SabouriS10}  are proposed. All the above methods are based on techniques using isolation of actors.
Rebeca is used for schedulability analysis of wireless sensor network applications \cite{DBLP:journals/sttt/KhamespanahSMA18}, protocol verification\cite{FOAC}, design exploration  and comparing routing algorithms \cite{DBLP:journals/eceasst/sharifiMMS13}. It is also used for lightweight preprocessing for agent-based simulation \cite{DBLP:journals/scp/BerardinisFJS18}. 


In the following section we explain what we mean by isolation of actors and how it can help in analysis. We then focus on a model %(FTTS) 
that is presented as the semantics of Timed Rebeca and can help by a significant amount of reduction in the state space while doing the analysis. We believe that similar techniques can be used in different analysis methods for event-based reactive isolated modules. 
%
In Section \ref{sec::DMC}, we present a technique used for analysis by distributed model checking which is specific for actors. The efficiency of the technique is checked for model checking Rebeca models.
%
Section \ref{sec::wrebeca} explains how we deployed special techniques to make analysis of  mobile adhoc networks possible.

%\noindent\textbf{Analysis of distributed systems and isolated actors.}
\section{Analysis of Distributed Systems and Isolated Actors}

The syntax of Timed Rebeca is showed in Figure \ref{fig::TRebecaSyntax}.
Timed Rebeca is an extension of Rebeca where we can model computational time, network delays, and periodic events \cite{DBLP:journals/scp/ReynissonSACJIS14,DBLP:conf/birthday/SirjaniK16}.
%
A Rebeca model consists of a set of reactive classes and a main part. In the \textit{main}, we declare the instances of the reactive classes as \textit{rebecs}. Rebec stands for reactive object, and is how actors are called in Rebeca. In a reactive class we define the known rebecs to whom we can send messages, the state variables, and the message servers. Message servers are the methods or event handlers of the class. The statements in Rebeca are very similar to Java.
The three keywords of \texttt{delay}, \texttt{after} and \texttt{deadline} are specific to Timed Rebeca.
Using \texttt{delay} we can model the computational time, using \texttt{after} we model network delays, and periodic events, and \texttt{deadline} is used to specify the timeout for handling the request we are sending out.

%\fixme{Syntax is messy}
%\Marjan{I should write a bit about the syntax and the extension in TRebeca Maybe this part on syntax and ... better go to the previous section?}

\fixme{Please read the following paragraph on isolation and see if it is correct and clear.}\Fatem{It was clear and correct to me}
%Active objects and 
Actors are encapsulated modules with no shared variables.
Our actors are reactive, there is no explicit receive and the messages (i.e. events) trigger the execution of the message servers (i.e. event handlers) when they are taken from the message queue.  Our actors are also asynchronous, when sending a message they are not blocked. 
So, there is no coupling via shared variables, no coupling because of waiting for another actor to return a value for a remote procedure call, and no coupling because of a context dependency caused by having a \textit{future}  construct in the language (\textit{futures} are mostly used in active object languages \cite{DBLP:journals/csur/BoerSHHRDJSKFY17}).
We call this decoupling of actors isolation, and use isolation of actors  in generating more efficient analysis techniques.
%
In Rebeca, we choose to have atomic execution of message servers (i.e. methods, or event handlers) which gives us a macro-step semantics and models a non-preemptive execution of the handlers.
Macro-step semantics, by itself, helps in reducing the state space size significantly.
The reason we can have atomic execution of message servers without loss of generality (in most cases\footnote{In some cases the behavior of a model may be different if we apply macro- or micro- semantics, or what we also call fine-grain and coarse-grain semantics. This discussion is out of scope of this paper.}) is the isolation of actors, and the fact that we assume non-preemptive execution of methods.
%\Marjan{I should add here that why we can have atomic method execution without loss of generality, and ... maybe how we can model preemption?}
%
Moreover, if we are only interested in the event-based properties we may be able to abstract even more and just keep the states that are followed by a transition which we are interested in. This type of reduction is not straight forward as we need to prove that we are preserving the order of the events while abstracting away some of the states and transitions (see the following section for more explanation). 
%This is what is done in partial order reduction.

For explaining our approach, we distinguish three levels of abstraction: the distributed software system itself with all the implementation details, the modeling language which is Rebeca here, and the generated state space which is built for the sake of analysis and  we model it as a state transition system. There are alternative ways for analysis, like using logical theorems and applying reasoning based on that, but here we use different variations of state transition systems.
We sometimes call the transition system the semantics of our model as it shows the behavior in a formal way.
%
Floating Time Transition System, explained in the following section, is a natural event-based semantics for timed actors, giving us a significant amount of reduction in the state space, using a non-trivial novel idea.
	